---
title: "T91-8_QB-8_A_SOI_6 Tidyverse"
author: "Trishelle Copeland-Johnson"
date: "February 24, 2018"
output: html_document

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Required Packages
The following packages are necessary for this project: 
```{r Required packages}
require(RCurl)
packageDescription("RCurl")
require(yaml)
packageDescription("yaml")
require(ggplot2)
packageDescription("ggplot2")
require(dplyr)
packageDescription("dplyr")
require(magrittr)
packageDescription("magrittr")
```

# Data Summary

```{r,echo=FALSE}
#Acquiring raw data----
df <- read.csv(text=getURL("https://raw.githubusercontent.com/PrayForEliza/T91-8_QB-8_A_SOI_6-Tidyverse/master/T91-8_QB-8_A_SOI_6.csv"),
                    header = T, skip = 9) 
df[] <- lapply(df,as.character)
colnames(df) <- df[1,]
df = df[-1, ]

```

## Tibble of raw data

```{r}
glimpse(df)
```

## Distribution of Wt%Total/Grid Spectrum

This histogram displays the total wt% (wt%Total) from each grid spectrum. Optimum un-normalized spectra have a total wt% is between 98% and 102%.

```{r, echo=FALSE}
df$`Weight%Total`=as.integer(as.character(df$`Weight%Total`))
wttots=ggplot(df,aes(x=df$'Weight%Total',fill=factor(..x..)))+geom_histogram(binwidth = 2)
plot(wttots)
```
